\documentclass[12pt]{article}

\usepackage{fouriernc}

\usepackage{hyperref}
\hypersetup
{
	colorlinks=true, %blue color for clickable%   
	urlcolor=blue
}

\begin{document}

\section{Introvert vs. Extrovert}
\begin{itemize}
	\item \href{https://www.quietrev.com/the-introvert-test/}{Introvert personality test}. According to the test, I am an introvert. Below is how they descibe introverts and extroverts. The description of an introvert mostly matches my personality. Although I do not deliberate a lot, at least not always, before taking decisions.
	\begin{itemize}
		\item Me, an introvert: Given the choice, you’ll devote your social energy to a small group of people you care about most, preferring a glass of wine with a close friend to a party full of strangers. You think before you speak, have a more deliberate approach to risk, and enjoy solitude. You feel energized when focusing deeply on a subject or activity that really interests you. When you’re in overly stimulating environments (too loud, too crowded, etc.) you tend to feel overwhelmed. You seek out environments of peace, sanctuary, and beauty; you have an active inner life and are at your best when you tap into its riches.
		\item Extroverts relish social life and are energized by interacting with friends and strangers alike. They’re typically assertive, go-getting, and able to seize the day. Extroverts are great at thinking on their feet; they’re relatively comfortable with conflict. Given the choice, extroverts usually prefer more stimulating environments that give them frequent opportunities to see and speak with others. When they’re in quiet environments, they’re prone to feeling bored and restless. They are actively engaged in the world around them and at their best when tapping into its energy.
	\end{itemize}
\end{itemize}

\end{document}